Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-11 index.Rmd
add slide w question before methods
added speaker note
added Figure 1 to background of results slides

---
class: inverse, center, middle
name: method

@@

@@

$~~$  
For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom

@@

In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). 
---
.center[

>>>>

# Does Crowdsourcing Data Analysis Improve the Credibility of Scientific Findings `r icon_style(icons::fontawesome("question-circle"), scale = 1, fill = "white")`

Lofty statements and worthy goals - empirical claim, but no evidence yet. that's what we'll be looking at today.
---
class: inverse, center, middle
name: method

@@

---
background-image: url("talk/Figure1.jpg")
background-position: 90% 60%
background-size: 40%

@@

$~~$  
$~~$

For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom

@@

In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). 
---
background-image: url("talk/Figure1.jpg")
background-position: 90% 60%
background-size: 40%
